\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-19 draft.tex
add SOCs to prop:2NNB proof, comment out for now

\vskip.2in
\noindent \un{Second Order Conditions} \\
When one non-negativity constraint binds, the bordered Hessian is 4x4.\\
		$\left|\begin{tabular}{cccc}
			0 & $\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ \\
			$\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
			$\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
			$\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
		\end{tabular} \right|\\$
$\hfill\blacksquare$

>>>>

\begin{comment}
\vskip.2in
\noindent \un{Second Order Conditions} \\
When one non-negativity constraint binds, the bordered Hessian is 4x4.\\
		$\left|\begin{tabular}{cccc}
			0 & $\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ \\
			$\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
			$\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
			$\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
		\end{tabular} \right|\\$

		\vskip.2in		
\noindent Evaluating the constraint terms, we have:\\
\begin{tabular}{cccc}
			0 & 0 & 0 & -1 \\
			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
		\end{tabular}

\vskip.2in
The second order condition is on the last two principal minors. The last must be negative. The next to last should then be positive.

Let's begin with the next-to-last principle minor, which is the determinant of the 3x3 matrix that is the upper-lefthand corner of this matrix. This is
	\[
	  0 + 0 + 0 - \left[0 + 0 + (-1)(-1)\frac{\partial^2 L}{\partial b(0)^2} \right] = - \frac{\partial^2 L}{\partial b(0)^2}
	\]
\begin{itemize}
	\item First we need the determinant of the next-to-last principal minor, the . This determinant should be positive. We can use the trick by which one copies the first two rows to the right of the matrix and then multiplies down the columns to the right and up the columns to the right (these terms get a negative sign). Then the determinant is
	  \[
		  0 + 0 + 0 - \left[0 + 0 + (-1)(-1)\frac{\partial^2 L}{\partial b(0)^2} \right] = - \frac{\partial^2 L}{\partial b(0)^2}
		\]
		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is non-negative
	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
		\[
		  0 \cdot \left|\text{something} \right| - (-1)\cdot 
			\left|\begin{array}{ccc}
				- 1 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right| + 0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right|
		\]
		\[ 
			=
			\left|\begin{array}{ccc}
				- 1 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		\]
		\[
		  = - 1 \cdot \left|\begin{array}{cc}
			\frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		\]
		\[
		  = - 1 \cdot \left(
			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
		\]
		\[
		  = \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
		\]

  We need this determinant to be non-positive, that is
		\[
		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 
		\]
	  The right hand side is positive because it's a square. Moreover, it is strictly positive because $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ is strictly positive: examine Equation~\ref{eq:xpartial}. Since $Z < 0$ in the case under examination, Equation~\ref{eq:xpartial} must be strictly positive. (This strengthens us from the negative semi-definite condition condition that supplies only a weak inequality).

		The left hand side must then be positive, and since we know that one term is positive from the previous principal minor result, the other must be positive as well. Thus both $X$ and $Y$ must be positive.
\end{itemize}
\end{comment}

$\hfill\blacksquare$
